### 2016-04-02 talk/icooolps2009-dotnet/intro.tex
start my talk

The main difference between the JIT compilers generated by PyPy and the
ones found in other projects like IronPython is that the latter compile
code at the method granularity: if on the one hand they can exploit
some of the knowledge gathered at runtime \davide{this contradicts what is stated in the intro} (e.g.\ the types of method
parameters), on the other hand they can do little to optimize most of
the operations inside, because few assumptions can be made about the
global state of the program.  The PyPy JITs, on the other hand, work at
a sub-method granularity, as described next.

>>>>

The main difference between the JIT compilers generated by PyPy and the
ones found in other projects like IronPython is that the latter compile
code at the method granularity: they can do little to optimize most of
the operations inside, because few assumptions can be made about the
types of the arguments and the
global state of the program.  The PyPy JITs, on the other hand, work at
a sub-method granularity, as described next.
